A Switching Planner for Combined Task and Observation Planning

### 2011-02-07 subarchitectures/planner.sa/trunk/src/latex/AAAI11/conc.tex
6-pages!
Moritz, can you add the new experimetns, and perhaps throw away some of the older ones.
Also made the correction in the concluding remarks

For use in an integrated continual planning and execution monitoring
system on a mobile robot platform, we developed a base planner that
switches between fast sequential and expensive decision-theoretic
planning. Given a DTPDDL model of the environment, sequential planning
is used to compute an initial deterministic sequential plan and
complementary runtime evolution of the decision process. That plan is
executed until testing of an assumption about the runtime state is
scheduled. At that point a contingent session performs some sensing
which determines whether or not the sequential session should be
allowed to continue, or otherwise acts to achieve the overall
objectives. We find our approach performs quickly and relatively
efficiently in large real-world task and observation planning
problems.

\Omit{
The most pressing item for future research, is to develop a scheme
whereby the serial planner can relax {\em executability} assumptions,
so that conformant (or semi-conformant) plans can be executed without
interruption by a contingent session. A more general criticism of
switching continual planning concerns interleaved sequential and
contingent sessions failing to make any progress towards the
objectives. For example, in the worst case we can have each sequential
session producing an identical plan, and each decision-theoretic
session rejecting it without further sensing. Although this has not
been an issue in our work so far, it must be dealt with rigorously
in the future. We suggest that a good way to mitigate this problem is
by developing a {\em motivational} component that maintains a {\em
dynamic} reward model whose limiting behaviour prevents that switching
deadlock.
}

>>>>

\vspace{-1ex}

For use in an integrated continual planning and execution monitoring
system on a mobile robot platform, we developed a base planner that
switches between fast sequential and expensive decision-theoretic
planning. Given a DTPDDL model of the environment, sequential planning
is used to compute an initial deterministic sequential plan and
complementary runtime evolution of the decision process. That plan is
executed until testing of an assumption about the runtime state is
scheduled. At that point a DT session performs some sensing
which determines whether or not the sequential session should be
allowed to continue, or otherwise acts to achieve the overall
objectives. We find our approach performs quickly and relatively
efficiently in a number of large real-world task and observation
planning problems.

\Omit{
The most pressing item for future research, is to develop a scheme
whereby the serial planner can relax {\em executability} assumptions,
so that conformant (or semi-conformant) plans can be executed without
interruption by a DT session. A more general criticism of
switching continual planning concerns interleaved sequential and
DT sessions failing to make any progress towards the
objectives. For example, in the worst case we can have each sequential
session producing an identical plan, and each decision-theoretic
session rejecting it without further sensing. Although this has not
been an issue in our work so far, it must be dealt with rigorously
in the future. We suggest that a good way to mitigate this problem is
by developing a {\em motivational} component that maintains a {\em
dynamic} reward model whose limiting behaviour prevents that switching
deadlock.
}
